A performance comparison of Dask and Spark for data-intensive neuroimaging pipelines

### 2019-07-25 latex/paper.tex
Worked on results :: histogram section

%%% INCREMENTATION %%%
%% worker
\subsection{Incrementation: Number of workers}
Figure~\ref{fig:inc_ms_worker} shows the makespan of the Incrementation application
for different numbers of workers and for different engines. The bars show the average
makespan over 5 repetitions while the error bars are the standard deviation. Overall,
there is no substantial makespan difference between the engines. Dask seems to have a
slight advantage over Spark, \SI{83.61}{\second} on average,
with Delayed and Futures being slightly better than Bags.

@@

%% Iterations
\subsection{Incrementation: Number of iterations}
Figure~\ref{fig:inc_ms_itr} shows the makespan of the application while
varying the number of iterations. Overall,  Spark and Dask APIs are once
again equivalent, although Dask Delayed and Futures are slightly faster
than Bags and Spark for 1 and 10 few iterations, and Fuures are faster than
Delayed, Bags and Spark for 100 iterations. Differences remain minor
though.

@@

\begin{figure*}[!htb]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/spark_inc_gantt.png}
        \caption{Spark}\label{fig:inc_spark_gantt}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/bag_inc_gantt.png}%
        \caption{Dask Bag}\label{fig:inc_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/delayed_inc_gantt.png}%
        \caption{Dask Delayed}\label{fig:inc_dask_delayed_gantt}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/futures_inc_gantt.png}%
        \caption{Dask Futures}\label{fig:inc_dask_futures_gantt}
    \end{subfigure}
    \caption{Gantt chart with 125 blocks, 10 iterations, \SI{4}{\second} delay, 8
    workers, 8 threads/worker}\label{fig:inc_gantt}
\end{figure*}

@@

@@

%%% BIDS EXAMPLE %%%
\subsection{BidsApp example: Number of workers}
Figure~\ref{fig:bids_ms_worker} shows the makespan of the application while varying
the amount of worker. Overall, there is no substantial difference between the
engines however Futures are always slightly faster. The performance difference between
Futures and the other APIs increases with the number of workers. The makespan scales
well with the increase in workers however the scaling reduces considerably when
reaching 8 workers. This is due to the IO requirement increasing with the number of
workers, since more tasks are read concurrently, and the application becomes more
data-intensive.

In Figure~\ref{fig:bids_tt_worker}, the total execution time of each function is
shown. \MD{Maybe mention why Spark overhead is so big.} Overall, the computation time
for the group analysis is equal for all engines and numbers of workers. Bag and
Delayed takes much longer to compute the participant analysis with 8 workers,
otherwise, the makespan is similar for all engines and numbers of workers. The overhead
increases as the number of workers increases. \MD{Check regression}

\MD{Depending on how the overhead is calculated spark overhead is either minimal or
gigantic. It is hard to determine which method should be used to calculate the
overhead for this application. For this application, since Spark has 2 job this
causes Spark to have different worker process for the different job and thus some job
have overlaping process ID while other are uniques (See
Figure~\ref{fig:bids_spark_gantt}).}

@@

% \begin{figure*}[!htb]
%     \centering
%     \begin{subfigure}[b]{\columnwidth}
%         \includegraphics[clip,width=\columnwidth]{images/spark_bids_gantt.png}
%         \caption{Spark}\label{fig:bids_spark_gantt}
%     \end{subfigure}
%     \hfill
%     \begin{subfigure}[b]{\columnwidth}
%         \includegraphics[clip,width=\columnwidth]{images/bag_bids_gantt.png}%
%         \caption{Dask Bag}\label{fig:bids_dask_bag_gantt}
%     \end{subfigure}
%     \\
%     \begin{subfigure}[b]{\columnwidth}
%         \includegraphics[clip,width=\columnwidth]{images/delayed_bids_gantt.png}%
%         \caption{Dask Delayed}\label{fig:bids_dask_delayed_gantt}
%     \end{subfigure}
%     \hfill
%     \begin{subfigure}[b]{\columnwidth}
%         \includegraphics[clip,width=\columnwidth]{images/futures_bids_gantt.png}%
%         \caption{Dask Futures}\label{fig:bids_dask_futures_gantt}
%     \end{subfigure}
%     \caption{Gantt chart with 8 workers}\label{fig:bids_gantt}
% \end{figure*}

>>>>

%%% INCREMENTATION %%%
%% worker
\subsection{Incrementation: Number of workers}
Figure~\ref{fig:inc_ms_worker} shows the makespan of the Incrementation application
for different numbers of workers and for different engines. The bars show the average
makespan over 3 repetitions while the error bars are the standard deviation. Overall,
there is no substantial makespan difference between the engines. Dask seems to have a
slight advantage over Spark, \SI{83.61}{\second} on average,
with Delayed and Futures being slightly better than Bags.

@@

%% Iterations
\subsection{Incrementation: Number of iterations}
Figure~\ref{fig:inc_ms_itr} shows the makespan of the application while
varying the number of iterations. Overall,  Spark and Dask APIs are once
again equivalent, although Dask Delayed and Futures are slightly faster
than Bags and Spark for 1 and 10 few iterations, and Futures are faster than
Delayed, Bags and Spark for 100 iterations. Differences remain minor
though.

@@

\begin{figure*}[!htb]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/spark_inc_gantt.png}
        \caption{Spark}\label{fig:inc_spark_gantt}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/bag_inc_gantt.png}%
        \caption{Dask Bag}\label{fig:inc_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/delayed_inc_gantt.png}%
        \caption{Dask Delayed}\label{fig:inc_dask_delayed_gantt}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/futures_inc_gantt.png}%
        \caption{Dask Futures}\label{fig:inc_dask_futures_gantt}
    \end{subfigure}
    \caption{Incrementation: Gantt chart with 125 blocks, 10 iterations, \SI{4}{\second}
delay, 8 workers, 8 threads/worker}\label{fig:inc_gantt}
\end{figure*}

@@

On Figure~\ref{fig:histo_tt_worker}, Dask engines have similar total execution time
when their number of workers varies, except for 8 worker where it incresase slightly.
On the other hand, Spark total execution time keeps increasing; especially at 8
workers. This is because Dask engines benefit more from additional workers.

@@

\subsection{Histogram (NumPy): Number of workers}
Figure~\ref{fig:histo_np_ms_worker}

From Figure~\ref{fig:histo_np_tt_worker}

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_np_worker.png}%
        \caption{Histogram (NumPy) makespan}\label{fig:histo_np_ms_worker}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_idle_np_worker.png}%
        \caption{Histogram (NumPy) total time}\label{fig:histo_np_tt_worker}
    \end{subfigure}
    \caption{125 blocks, 8 threads/worker}
\end{figure}

\subsection{Histogram (NumPy): Number of blocks}
Figure~\ref{fig:histo_np_ms_block}

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_np_block.png}%
        \caption{Histogram (NumPy) makespan}\label{fig:histo_np_ms_block}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_idle_np_block.png}%
        \caption{Histogram (NumPy) total time}\label{fig:histo_np_tt_block}
    \end{subfigure}
    \caption{8 workers, 8 threads/worker}
\end{figure}

%%% BIDS EXAMPLE %%%
\subsection{BidsApp example: Number of workers}
Figure~\ref{fig:bids_ms_worker} shows the makespan of the application while varying
the amount of worker. Overall, there is no substantial difference between the
engines. The makespan scales well with the increase in workers however the scaling
reduces considerably when reaching 8 workers. This is due to the IO requirement
increasing with the number of workers --- more tasks are read concurrently and
the application becomes more data-intensive.

In Figure~\ref{fig:bids_tt_worker}, the total execution time of each function is
shown. Overall, there is no significant difference between the engines. Each engines
have similar total time independently of their number of worker. This is because the
engines scale almost linearly. The overhead increase slowly as the number of workers
increases. This is due to more communication between the scheduler and workers as
well as inter-worker communication.

@@

\begin{figure*}[!htb]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/spark_bids_gantt.png}
        \caption{Spark}\label{fig:bids_spark_gantt}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/bag_bids_gantt.png}%
        \caption{Dask Bag}\label{fig:bids_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/delayed_bids_gantt.png}%
        \caption{Dask Delayed}\label{fig:bids_dask_delayed_gantt}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/futures_bids_gantt.png}%
        \caption{Dask Futures}\label{fig:bids_dask_futures_gantt}
    \end{subfigure}
    \caption{BIDS App example: Gantt chart with 8 workers}\label{fig:bids_gantt}
\end{figure*}
